The Importance of Affective States in Privacy Calculus

### 2021-05-01 submission.tex
Findings for VPN usage

\begin{figure}[H]
    \includegraphics[width=0.5\textwidth]{univariate social media practices}
    \caption{Respondents' actual privacy practices regarding on social media.
	Only respondents who indicated concern about social media privacy were
	asked to answer this question.}
    \label{Univariate Distribution Respondent Concerns}
\end{figure}
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}

>>>>

\begin{figure}[H]
    \includegraphics[width=0.5\textwidth]{univariate social media practices}
    \caption{Respondents' actual privacy practices regarding on social media.
	Only respondents who indicated concern about social media privacy were
	asked to answer this question.}
    \label{Univariate Distribution Respondent Concerns}
\end{figure}

\subsection{VPN Usage}
We exclude from our analyses one respondent who did not know what a VPN was.

Strong relationship between \emph{how an individual feels when using a VPN and
whether they use one}, with a gamma value of .786. Relatively significant
relationship (p=.169) given sample size.  Relatively significant Chi-Square
(p=.107), despite not ruling out null hypothesis conclusively.

Perfect correlation between \emph{how an individual feels while setting up a
VPN, and whether they use one}. Relatively significant relationship (p=.169)
given sample size. Relatively significant Chi-Square (p=.211), despite not
ruling out null hypothesis conclusively.

With a gamma value of .973, there eists a near perfect relationship between
\emph{how an individual feels after setting up a VPN and how they feel when
their device is using a VPN}. This relationship is highly significant
(p<.001,***), and the chi-square test of significance rules out the null
hypothesis (p<.001,***).

A perfect inverse relationship exists between \emph{how somebody feels while
setting up a VPN and how they feel if their device is not using one}. It is
relatively significant (p=.139) given the small sample size.  Relatively
significant Chi-Square (p=.183), despite not ruling out null hypothesis
conclusively.

\section{Discussion}
\subsection{Ad Tracking}
\textbf{TODO}
The inability to rule out the null hypothesis is likely due to the small sample
size of 34 respondents who were asked these questions.

%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{biblio}
